Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach

### 2021-12-20 Manuscript/FLPhish(Trans).tex
修改Yuan Zhang提出的一些问题

\author{Beibei~Li,~\IEEEmembership{Member,~IEEE,}
        Peiran~Wang,~\IEEEmembership{Student Member,~IEEE,}
        Qinglei~Kong,~\IEEEmembership{Student Member,~IEEE,}
        Yuan~Zhang,~\IEEEmembership{Member,~IEEE,}
        and~Rongxing~Lu,~\IEEEmembership{Fellow,~IEEE}
\thanks{This paper is the extended vision of the paper, `FLPhish: Reputation-Based Phishing Byzantine Defense in Ensemble Federated Learning', which was published in IEEE ISCC 2021, and was awarded `Best Paper Award' in this conference.}
\thanks{B. Li and P. Wang are with the School of Cyber Science and Engineering, Sichuan Universsity, Chengdu, Sichuan, China 610065 China. Email: libeibei@scu.edu.cn; wangpeiran@stu.scu.edu.cn.}
\thanks{Q. Kong is with the Future Network of Intelligence Institute, The Chinese University of Hong Kong, Shenzhen 518172, China, and also with The University of Science and Technology of China, Hefei 230052, China. Email: kql8904@163.com.}
\thanks{Y. Zhang is with the Center for Cyber Security, School of Computer Science and Engineering, University of Electronic Science and Technology of China, Chengdu, China 610054. Email: zy\_loye@126.com.}
\thanks{R. Lu is with the Faculty of Computer Science, University of New Brunswick, Fredericton, NB, Canada E3B 5A3. Email: rlu1@unb.ca.}
}

@@

\begin{abstract}
  Federated Learning, a new distributed machine learning scheme, is gaining popularity as the demand for personal privacy grows. Nonetheless, the implementation of FL is still vulnerable to Byzantine attacks, which can bring significant hazards to the global model aggregation process. Byzantine attacks are extremely difficult to defend against in the current FL scheme. In this study, we present a novel reputation-based phishing scheme (called FLPhish) in defending against Byzantine attacks in Ensemble FL. First, we design a new Ensemble FL architecture, to enable flexible implementation of various types of deep learning models in different clients. Second, we craft a phishing mechanism for the Ensemble FL architecture to identify Byzantine attacks. Furthermore, a reputation mechanism based on Bayes's theorem is presented to assess each client's level of confidence. Last, we propose two aggregation techniques in FLPhish: FLPhish-threshold and FLPhish-weight. FLPhish is tested with varying proportions of Byzantine clients and varying degrees of distribution imbalance. Extensive experiments under various situations demonstrates the proposed FLPhish's great efficacy in resisting Byzantine attacks in Ensemble FL.
\end{abstract}

\begin{IEEEkeywords}
Federated learning, ensemble learning, bayesian inference reputation, phishing.
\end{IEEEkeywords}

@@

\par Former researchers have offered certain Byzantine-robust techniques to deal with malevolent Byzantine clients in FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}. In the presence of a bounded number of malicious clients, Byzantine-robust approaches try to develop a global model with high accuracy. According to their different mechanisms, we divide Byzantine-robust approaches into two major kinds. The first (named Byzantine-Detection) is based on the creation of a Byzantine-robust aggregation rule that distinguishes questionable customers from benign clients. The server then eliminates the suspected clients' gradient updates from the aggregate process. For instance, in DRACO, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}. Another group of Byzantine-robust approaches (dubbed Byzantine-Tolerance) aims to ensure that the aggregation process is tolerant of Byzantine clients' poisoned updates without excluding Byzantine clients like Median \cite{ref_16_defense}. The FL server sorts the values of each parameter based on Median and selects the median value of each parameter as the value to be used in global model updates. Recent research, however, suggests that current approaches are still vulnerable to Byzantine attacks \cite{ref_06_model}. We present a novel reputation-based phishing scheme (called FLPhish) in defending against Byzantine attacks in Ensemble FL. Our contributions are four-folds:
\begin{itemize}
  \item First, we design a new FL architecture, Ensemble Federated Learning (called Ensemble FL). Ensemble FL utilizes an unlabeled dataset to replace the gradient updates in traditional FL. This architecture supports different types of deep learning models in each client and makes FL more flexible.
  \item Second, we craft a `phishing' method based on Ensemble FL to detect Byzantine attacks. The `phishing' method employs the labeled dataset to detect the potential Byzantine clients in the Ensemble FL system. It preserves the security of Ensemble FL.
  \item Third, we present a bayesian inference-based reputation mechanism to promote FLPhish's aggregation. The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine clients. The reputation mechanism helps FLPhish identify the Byzantine clients more accurately.
  \item Last, we propose two aggregation algorithms FLPhish-threshold and FLPhish-weight to aggregate the predictions of the FL clients, based on reputation mechanism. FLPhish using FLPhish-threshold identifies the clients with low reputation values as Byzantine clients, while FLPhish with FLPhish-weight utilizes the reputation value of each client as its aggregation weight to participate aggregation process. These two algorithms contribute to the robustness of FLPhish.
\end{itemize}

@@

  \par \textit{1)} Inspired by the idea of ensemble learning, we build a new FL architecture called Ensemble FL. It reduces the network transfer cost and provide more opportunities for us to counter Byzantine attacks in FL.
  \par \textit{2)} Our proposed Ensemble FL architecture lacks protection against Byzantine attacks. Since the clients in FL can not be fully trusted, we urgently require an efficient way to tackle malicious Byzantine clients. Thus, we present a phishing-based model to guard against Byzantine attacks in our proposed Ensemble FL system.
  \par \textit{3)} To accurately assess clients' behaviors, we further propose an effective bayesian-based reputation scheme based on our phishing-based model to spot Byzantine attacks compromised by malicious users.
  \par \textit{4)} Furthermore, we propose two aggregation algorithms in FLPhish, FLPhish-threshold and FLPhish-weight to aggregate the predictions of the FL clients, which can further enhance FLPhish's defending ability against Byzantine attacks.

@@

\subsection{Bayesian Inference-based Reputation Mechanism}
Server $s$ maintains a reputation list which records the reputation of all the clients $C$ in the model. Let $X_i$ be the reputation of the $c_i$ client which represents $s$'s belief that how likely client $c_i$ is a Byzantine client. The computation of $X_i$ is based on the accuracy $a_i^t$ of client $c_i$ from the 1st round to the $t$th round. Every time a new update of client $c_i$ comes to server $s$, $s$ uses the accuracy $a_i^t$ to update the $X_i$.
\par Initially, the reputation is neutral. Each client $c_i$ is considered a benign client by server $s$ with a probability of 50\%. When a new update $\mathbf{k_i^t}$ comes to the server $s$, the reputation is updated by the $s$. When the reputation is lower than the threshold $r$, $s$ considers the client $c_i$ as a Byzantine client officially and discards the update coming from the client $c_i$. The updates of the client $c_i$ are reconsidered in the aggregation when the $X_i$ exceeds the threshold $r$.
\par We employ bayesian inference to construct our reputation mechanism. Each data prediction made by client $c_i$ faces two situations: wrong predictions or correct predictions. Thus, the use of binomial parameter distributions becomes a natural choice for our reputation mechanism. Let $Y_i$ be the event that the number of wrong predictions and correct predictions made by client $c_i$ is $\alpha_i$ and $\beta_i$. Given $X_i=\gamma_i$, then the conditional probability is 
\begin{equation}
    Pr(Y_i|X_i=\gamma _i)=\left ( \frac{\alpha _i+\beta _i}{\alpha _i} \right )\gamma {_{i}}^{\alpha_i}\left ( 1-\gamma_{i} \right )^{\beta_{i}}\label{equation_1}.
\end{equation}
$\alpha_i$ and $\beta_i$ is the available evidence for the estimation of the $X$. $\gamma_i$ is unknown. Equation \ref{equation_1} indicates the likelihood function for $X$. According to bayes' theory, we compute the posterior probability as
\begin{equation}
    Pr(X_i=\gamma _i|Y_i)=\frac{Pr\left ( Y_{i}|X_{i}=\gamma_{i} \right )Pr(X_{i}=\gamma_{i})}{\int_{0}^{1}Pr\left ( Y_{i}|X_{i}=x \right )Pr(X_{i}=x)dx}\label{equation_2}.
\end{equation}
As the posterior probability function is given by our analysis, the final value for the expectation value of reputation $X$ is computed as
\begin{equation}
    E(X)=\int_{0}^{1}\frac{Pr\left ( Y_{i}|X_{i}=\gamma_{i} \right )Pr(X_{i}=\gamma_{i})}{\int_{0}^{1}Pr\left ( Y_{i}|X_{i}=x \right )Pr(X_{i}=x)dx}\gamma_{i}d\gamma_{i}\label{equation_3}.
\end{equation}
Furthermore, we decide to use the binomial parameter beta distribution to describe the distribution of X. Assume X is a random variable of the beta distribution with the parameters $(\alpha, \beta)$. Therefore the density function is
\begin{equation}
    f(x,\alpha,\beta)=\frac{1}{B(\alpha,\beta)}x^{\alpha-1}(1-x)^{\beta-1}\label{equation-4}.
\end{equation}
$B$ function is the beta function. Therefore we compute the expectation of $X$ as
\begin{equation}
    E(x)=\frac{\alpha}{\alpha+\beta}.
\end{equation}

>>>>

\author{Beibei~Li,~\IEEEmembership{Member,~IEEE,}
        Peiran~Wang,~\IEEEmembership{Student Member,~IEEE,}
        Qinglei~Kong,~\IEEEmembership{Student Member,~IEEE,}
        Yuan~Zhang,~\IEEEmembership{Member,~IEEE,}
        and~Rongxing~Lu,~\IEEEmembership{Fellow,~IEEE}
\thanks{This paper is the extended vision of the paper, `FLPhish: Reputation-Based Phishing Byzantine Defense in Ensemble Federated Learning', which was published in IEEE ISCC 2021, and was awarded `Best Paper Award' in this conference.}
\thanks{B. Li and P. Wang are with the School of Cyber Science and Engineering, Sichuan Universsity, Chengdu, Sichuan, China 610065 China. Email: libeibei@scu.edu.cn; wangpeiran@stu.scu.edu.cn.}
\thanks{Q. Kong is with the Future Network of Intelligence Institute, The Chinese University of Hong Kong, Shenzhen 518172, China, and also with The University of Science and Technology of China, Hefei 230052, China. Email: kql8904@163.com.}
\thanks{Y. Zhang is with the School of Computer Science and Engineering, University of Electronic Science and Technology of China, Chengdu, China 610054. Email: zy\_loye@126.com.}
\thanks{R. Lu is with the Faculty of Computer Science, University of New Brunswick, Fredericton, NB, Canada E3B 5A3. Email: rlu1@unb.ca.}
}

@@

\begin{abstract}
  Federated Learning, a new distributed machine learning architecture, is gaining popularity as the demand for personal privacy grows. Nonetheless, the implementation of FL is still vulnerable to Byzantine attacks, which can bring significant hazards to the global model aggregation process. Byzantine attacks are extremely difficult to defend against in current FL. In this paper, we present a reputation-based phishing scheme (FLPhish) to defend Byzantine attacks in Ensemble FL. First, we design a new Ensemble FL architecture, which is compatible with different deep learning models in different clients. Second, we craft a phishing mechanism for the Ensemble FL architecture to identify Byzantine attacks. Furthermore, a reputation mechanism based on Bayesian inference is presented to measure each client's level of confidence. Last, we propose two aggregation techniques in FLPhish: FLPhish-threshold and FLPhish-weight. FLPhish is tested with varying proportions of Byzantine clients and varying degrees of distribution imbalance. Extensive experiments under various situations demonstrates the proposed FLPhish's great efficacy in resisting Byzantine attacks in Ensemble FL.
\end{abstract}

\begin{IEEEkeywords}
Federated learning, ensemble learning, Bayesian inference reputation, phishing.
\end{IEEEkeywords}

@@

\par Former researchers have offered certain Byzantine-robust techniques to deal with malevolent Byzantine clients in FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}. In the presence of a bounded number of malicious clients, Byzantine-robust approaches try to develop a global model with high accuracy. According to their different mechanisms, we divide Byzantine-robust approaches into two major kinds. The first (named Byzantine-Detection) is based on the creation of a Byzantine-robust aggregation rule that distinguishes questionable customers from benign clients. The server then eliminates the suspected clients' gradient updates from the aggregate process. For instance, in DRACO, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}. Another group of Byzantine-robust approaches (dubbed Byzantine-Tolerance) aims to ensure that the aggregation process is tolerant of Byzantine clients' poisoned updates without excluding Byzantine clients like Median \cite{ref_16_defense}. The FL server sorts the values of each parameter based on Median and selects the median value of each parameter as the value to be used in global model updates. Recent research, however, suggests that current approaches are still vulnerable to Byzantine attacks \cite{ref_06_model}. We present a novel reputation-based phishing scheme (called FLPhish) in defending against Byzantine attacks in Ensemble FL. Our contributions are four-folds:
\begin{itemize}
  \item We design a new FL architecture, Ensemble Federated Learning (called Ensemble FL). Ensemble FL utilizes an unlabeled dataset to replace the gradient updates in traditional FL. This architecture supports different types of deep learning models in each client and makes FL more flexible.
  \item We craft a `phishing' method based on Ensemble FL to detect Byzantine attacks. The `phishing' method employs the labeled dataset to detect the potential Byzantine clients in the Ensemble FL system. It preserves the security of Ensemble FL.
  \item We present a Bayesian inference-based reputation mechanism to promote FLPhish's aggregation. The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine clients. The reputation mechanism helps FLPhish identify the Byzantine clients more accurately.
  \item We propose two aggregation algorithms FLPhish-threshold and FLPhish-weight to aggregate the predictions of the FL clients, based on reputation mechanism. FLPhish using FLPhish-threshold identifies the clients with low reputation values as Byzantine clients, while FLPhish with FLPhish-weight utilizes the reputation value of each client as its aggregation weight to participate aggregation process. These two algorithms contribute to the robustness of FLPhish.
\end{itemize}

@@

  \par \textit{1)} Inspired by the idea of ensemble learning, we build a new FL architecture called Ensemble FL. It reduces the network transfer cost and provide more opportunities for us to counter Byzantine attacks in FL.
  \par \textit{2)} Our proposed Ensemble FL architecture lacks protection against Byzantine attacks. Since the clients in FL can not be fully trusted, we urgently require an efficient way to tackle malicious Byzantine clients. Thus, we present a phishing-based model to guard against Byzantine attacks in our proposed Ensemble FL system.
  \par \textit{3)} To accurately assess clients' behaviors, we further propose an effective Bayesian-based reputation scheme based on our phishing-based model to spot Byzantine attacks compromised by malicious users.
  \par \textit{4)} Furthermore, we propose two aggregation algorithms in FLPhish, FLPhish-threshold and FLPhish-weight to aggregate the predictions of the FL clients, which can further enhance FLPhish's defending ability against Byzantine attacks.

@@

\subsection{Bayesian Inference-based Reputation Mechanism}
Server $s$ maintains a reputation list which records the reputation of all the clients $C$ in the model. Let $X_i$ be the reputation of the $c_i$ client which represents $s$'s belief that how likely client $c_i$ is a Byzantine client. The computation of $X_i$ is based on the accuracy $a_i^t$ of client $c_i$ from the 1st round to the $t$th round. Every time a new update of client $c_i$ comes to server $s$, $s$ uses the accuracy $a_i^t$ to update the $X_i$.
\par Initially, the reputation is neutral. Each client $c_i$ is considered a benign client by server $s$ with a probability of 50\%. When a new update $\mathbf{k_i^t}$ comes to the server $s$, the reputation is updated by the $s$. When the reputation is lower than the threshold $r$, $s$ considers the client $c_i$ as a Byzantine client officially and discards the update coming from the client $c_i$. The updates of the client $c_i$ are reconsidered in the aggregation when the $X_i$ exceeds the threshold $r$.
\par We employ Bayesian inference to construct our reputation mechanism. Each data prediction made by client $c_i$ faces two situations: wrong predictions or correct predictions. Thus, the use of binomial parameter distributions becomes a natural choice for our reputation mechanism. Let $Y_i$ be the event that the number of wrong predictions and correct predictions made by client $c_i$ is $\alpha_i$ and $\beta_i$. Given $X_i=\gamma_i$, then the conditional probability is 
\begin{equation}
    Pr(Y_i|X_i=\gamma _i)=\left ( \frac{\alpha _i+\beta _i}{\alpha _i} \right )\gamma {_{i}}^{\alpha_i}\left ( 1-\gamma_{i} \right )^{\beta_{i}}\label{equation_1}.
\end{equation}
$\alpha_i$ and $\beta_i$ is the available evidence for the estimation of the $X$. $\gamma_i$ is unknown. Equation \ref{equation_1} indicates the likelihood function for $X$. According to Bayesian inference we compute the posterior probability as
\begin{equation}
    Pr(X_i=\gamma _i|Y_i)=\frac{Pr\left ( Y_{i}|X_{i}=\gamma_{i} \right )Pr(X_{i}=\gamma_{i})}{\int_{0}^{1}Pr\left ( Y_{i}|X_{i}=x \right )Pr(X_{i}=x)dx}\label{equation_2}.
\end{equation}
As the posterior probability function is given by our analysis, the final value for the expectation value of reputation $X$ is computed as
\begin{equation}
    E(X)=\int_{0}^{1}\frac{Pr\left ( Y_{i}|X_{i}=\gamma_{i} \right )Pr(X_{i}=\gamma_{i})}{\int_{0}^{1}Pr\left ( Y_{i}|X_{i}=x \right )Pr(X_{i}=x)dx}\gamma_{i}d\gamma_{i}\label{equation_3}.
\end{equation}
Furthermore, we decide to use the binomial parameter beta distribution to describe the distribution of X. Assume X is a random variable of the beta distribution with the parameters $(\alpha, \beta)$. Therefore the density function is
\begin{equation}
    f(x,\alpha,\beta)=\frac{1}{B(\alpha,\beta)}x^{\alpha-1}(1-x)^{\beta-1}\label{equation-4}.
\end{equation}
$B$ function is the beta function. Therefore we compute the expectation of $X$ as
\begin{equation}
    E(x)=\frac{\alpha}{\alpha+\beta}.
\end{equation}
